Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-11 2_relatedwork/relatedwork.tex
no message

Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing}, delta analysis \cite{esgin2011delta,esgin2013sequence} and mismatch patterns \cite{dijkman2007mismatch}. In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations that execute the same tasks.

>>>>

Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing,weidlich2011variability}, ontology analysis \cite{pascalau2010variants}, delta analysis \cite{esgin2011delta,esgin2013sequence,hallerbach2010variability} and mismatch patterns \cite{dijkman2007mismatch}. In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations that execute the same tasks.

### 2015-11-11 4_methodology/methodology.tex
no message

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

>>>>

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. Considering the fact that the process models may not be defined beforehand or outdated to reflect latest state of the process, they are mined from event logs. However, if there are process models that represent the event logs, this stage can be skipped. In order to mine process models, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}
